---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# adeckstats

<!-- badges: start -->

<!-- badges: end -->

The goal of adeckstats is to ...

## Installation

You can install the development version of adeckstats like so:

``` r
devtools::install_github('norepoforyousucker')
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(adeckstats)
adeckstats::adeck_binarysearch(c(1,2,3),2)
```

---- $SPECIAL TOPICS$ ------

A look at special topics I am learning and using to develop this package. This is the ultimate intersection of learning and development.

---- $ALGORITHMS$ ------

## Search Algorithms

The aim is to do one a day and master algorithms, starting with search algorithms.

### Binary Search Algorithm

```{r}
adeckstats::adeck_binarysearch(c(1,2,3,4,5), 1)
```

Time and Space Complexity

Time Complexity:

Drivers are Input size (n), Basic operations (e.g. comparisons in a sorting algorithm), and Asymptotic analysis (behavior of the algorithm as n approaches infinity).

Calculating Time complexity involves:

-   Identify n
-   count the basic operations
-   combine operations (add for sequential ops and product for nest ops)
-   Use asymptotic notation focusing on the term that grows fastest and n increases

Space Complexity:

The binary search algorithms halves the search space and this algorithm really sank in when i understood this benefit.
